### 2019-10-03 paper/paper.tex
More work in progress

\begin{equation} \label{eq:Karb2DExt_dc}
\frac{\partial c_i(\mb{x},t)}{\partial t} =-\alpha c_i(\mb{x},t) +\beta  \left(1 - \sum_{j=1}^{N} c_j(\mb{x}, t)\right)[a_i(\mb{x},t)]^k.
\end{equation}

Accordingly, when the final term evaluates to zero, the density of
thalamocortical connections decays exponentially at a rate given by the decay
constant $\alpha$. This occurs where the density of connections over all
thalamic projections sum to one. Otherwise, the connection density is assumed
to vary non-linearly ($k>1$) with changes in the axon branching density.

@@

There exists an element of competition in the model system specified by
Eqns. \ref{eq:Karb2DExt_dc} \& \ref{eq:Karb2DExt_da}.

@@

\section{Karbowski system with N TCs and M gradients}
%
\begin{equation} \label{eq:Karb2D_dc}
\frac{\partial c_i(\mb{x},t)}{\partial t} = -\alpha c_i(\mb{x},t) + \beta n(\mb{x},t)
[a_i(\mb{x},t)]^k
\end{equation}
%
\begin{equation} \label{eq:Karb2D_conserve}
n(\mb{x},t) = 1 - \sum_{i=1}^{N} c_i(\mb{x}, t)
\end{equation}
%
\begin{equation} \label{eq:Karb2D_da}
\frac{\partial a_i(\mb{x},t)}{\partial t}
= \nabla\vcdot\mb{J}_i(\mb{x},t) - \frac{\partial c_i(\mb{x},t)}{\partial t}
\end{equation}

@@

\section{Karbowski system with N TCs and M gradients plus competition}

>>>>

\begin{equation} \label{eq:Karb2DExt_dc}
\frac{\partial c_i(\mb{x},t)}{\partial t} =-\alpha c_i(\mb{x},t) +\beta  \left(1 - \sum_{i'=1}^{N} c_{i'}(\mb{x}, t)\right)[a_i(\mb{x},t)]^k.
\end{equation}

Accordingly, when the final term evaluates to zero, the density of
thalamocortical connections decays exponentially at a rate given by the decay
constant $\alpha$. This occurs where the density of connections over all
thalamic projections sum to one; interpreted as a state in which all of the
available synaptic receptors within the cortical dendritic trees are
occupied. Otherwise, the connection density is assumed to vary non-linearly
($k>1$) with the axon branching density.

@@

There exists an element of competition in the model system specified by
Eqns. \ref{eq:Karb2DExt_dc} \& \ref{eq:Karb2DExt_da}. The term $\left(1 -
\sum_{i=1}^{N} c_i(\mb{x}, t)\right)$ ensures that once the available synaptic
receptors in a region have been fully occupied, say by thalamocortical types
$i=2$ and $i=3$, there is no longer the possibility for type $i=1$ to form any
synapses. This competition turns out to be relatively weak, because it does
not strongly affect the branching density in that region; two or more TC axon
types can be branching equally in the region, leading to roughly equal numbers
of connections being made up until the connection limit is reached.

To introduce an element of competition between the branching of
thalamocortical axon types, we introduced the new term $\chi$ given by
%
\begin{equation} \label{eq:branch_comp}
\chi(\mb{x}, t) = - \frac{\epsilon  a_i}{N-1} \sum_{i' \ne i}^{N} a_{i'}(\mb{x}, t)
\end{equation}
%
which leads to a reduction in the rate of increase of branching density for
axon type $i$ in regions where the branching density of \e{other} axon
types is high.

This introduces a new parameter, $\epsilon$, which governs the
strength of the branching competition. The factor $1/(N-1)$ ensures that the
branching competition strength scales with the number of TC axons in the
system.

@@

\section*{App 1: Karbowski system with N TCs and M gradients}
%
\begin{equation} \label{eq:Karb2D_dc}
\frac{\partial c_i(\mb{x},t)}{\partial t} = -\alpha c_i(\mb{x},t) + \beta n(\mb{x},t)
[a_i(\mb{x},t)]^k
\end{equation}
%
\begin{equation} \label{eq:Karb2D_conserve}
n(\mb{x},t) = 1 - \sum_{i=1}^{N} c_i(\mb{x}, t)
\end{equation}
%
\begin{equation} \label{eq:Karb2D_da}
\frac{\partial a_i(\mb{x},t)}{\partial t}
= \nabla\vcdot\mb{J}_i(\mb{x},t) - \frac{\partial c_i(\mb{x},t)}{\partial t}
\end{equation}

@@

\section{App 2: Karbowski system with N TCs and M gradients plus competition}
